Flux2022

### 2022-04-21 DataSetup.Rmd
Added ABCD baseline model (initial version)
Updated for baseline version, added talapas script

@@

renamed_smri <- smri_baseline %>% 

@@

#Create empty columns to match feature list
renamed_smri[,"FS_BrainSeg_Vol"] <- NA
renamed_smri[,"FS_BrainSeg_Vol_No_Vent"] <- NA
renamed_smri[,"FS_BrainSeg_Vol_No_Vent_Surf"] <- NA
renamed_smri[,"FS_SupraTentorial_Vol_No_Vent"] <- NA
renamed_smri[,"FS_SupraTentorial_No_Vent_Voxel_Count"] <- NA
renamed_smri[,"FS_Mask_Vol"] <- NA
renamed_smri[,"FS_BrainSegVol_eTIV_Ratio"] <- NA
renamed_smri[,"FS_MaskVol_eTIV_Ratio"] <- NA
renamed_smri[,"FS_L_Vessel_Vol"] <- NA
renamed_smri[,"FS_L_ChoroidPlexus_Vol"] <- NA
renamed_smri[,"FS_R_Vessel_Vol"] <- NA
renamed_smri[,"FS_R_ChoroidPlexus_Vol"] <- NA
renamed_smri[,"FS_OpticChiasm_Vol"] <- NA
renamed_smri[,"FS_Total_GM_Vol"] <- NA

@@

#Convert to numeric
renamed_smri[,6:279] <- sapply(renamed_smri[,6:279],as.numeric)
renamed_smri <- renamed_smri %>% 
  mutate(interview_age = as.numeric(interview_age)/12)

>>>>

#parent sum scores abcd_mhp01
#youth sum scores abcd_mhy01

@@

renamed_smri_baseline <- smri_baseline %>% 

@@

#Create empty columns to match feature list
renamed_smri_baseline[,"FS_BrainSeg_Vol"] <- NA
renamed_smri_baseline[,"FS_BrainSeg_Vol_No_Vent"] <- NA
renamed_smri_baseline[,"FS_BrainSeg_Vol_No_Vent_Surf"] <- NA
renamed_smri_baseline[,"FS_SupraTentorial_Vol_No_Vent"] <- NA
renamed_smri_baseline[,"FS_SupraTentorial_No_Vent_Voxel_Count"] <- NA
renamed_smri_baseline[,"FS_Mask_Vol"] <- NA
renamed_smri_baseline[,"FS_BrainSegVol_eTIV_Ratio"] <- NA
renamed_smri_baseline[,"FS_MaskVol_eTIV_Ratio"] <- NA
renamed_smri_baseline[,"FS_L_Vessel_Vol"] <- NA
renamed_smri_baseline[,"FS_L_ChoroidPlexus_Vol"] <- NA
renamed_smri_baseline[,"FS_R_Vessel_Vol"] <- NA
renamed_smri_baseline[,"FS_R_ChoroidPlexus_Vol"] <- NA
renamed_smri_baseline[,"FS_OpticChiasm_Vol"] <- NA
renamed_smri_baseline[,"FS_Total_GM_Vol"] <- NA

@@

#Convert to numeric
renamed_smri_baseline[,6:279] <- sapply(renamed_smri_baseline[,6:279],as.numeric)
renamed_smri_baseline <- renamed_smri_baseline %>% 
  mutate(interview_age = as.numeric(interview_age)/12)

save(renamed_smri_baseline, file="renamed_smri_baseline.Rda")

Feature list template

### 2022-04-21 Flux2022.Rmd
Updated for baseline version, added talapas script

sample_1 <- brainage_pds[sample_ind, ]
sample_2 <- brainage_pds[-sample_ind, ]
```

@@

Model Figures
```{r}
plot_model(baseline_puberty_y_mean_1, type="pred", terms = "youth_mean")

plot_model(baseline_puberty_p_mean_1, type="pred", terms = "parent_mean")

plot_model(baseline_cognition_1, type="pred", terms = "nihtbx_totalcomp_agecorrected")
plot_model(baseline_cognition_2, type="pred", terms = "nihtbx_totalcomp_agecorrected")

>>>>

sample_1 <- brainage_pds[sample_ind, ]
sample_2 <- brainage_pds[-sample_ind, ]

#t test for age differences
t.test(sample_1$interview_age, sample_2$interview_age)

#Save samples

save(sample_1, file="Sample1.Rda")
save(sample_2, file = "Sample2.Rda")

@@

Model Figures
```{r}
plot_model(baseline_puberty_y_mean_1, type="pred", terms = "youth_mean", colors = "#67322e", title = "Predicted Gap") +
  theme_sjplot()

plot_model(baseline_puberty_p_mean_1, type="pred", terms = "parent_mean", title = "Predicted Gap") +
  theme_sjplot()

plot_model(baseline_cognition_1, type="pred", terms = "nihtbx_totalcomp_agecorrected", title = "Predicted Gap")+
  theme_sjplot()

plot_model(baseline_cognition_2, type="pred", terms = "nihtbx_totalcomp_agecorrected")
